Lightning Talk: Software Citation: Process, Principles, and Implementation

### 2016-08-02 meetings/WSSSPE4-lightning-talk/WSSSPE4-lightning-talk.tex
updating text+URL to show resubmitted version of principles paper fixing columns on last page

@@

The final draft paper was then submitted to  PeerJ Computer Science , published as a PeerJ preprint \cite{bib4}, and posted on the FORCE11 website \cite{bib2}. Initial review comments were provided July 8, 2016, and the working group chairs are currently discussing them. Our goal is to have a final version of the paper accepted by WSSSPE4.

@@

\bibitem{bib1}
FORCE11 Software Citation Working Group, ``Software citation use cases,'' \url{https://docs.google.com/document/d/1dS0SqGoBIFwLB5G3HiLLEOSAAgMdo8QPEpjYUaWCvIU}, 2016. Accessed: 2016-07-10.
\bibitem{bib2} 
A.~M.~Smith AM, D.~S.~Katz, K.~E.~Niemeyer, and FORCE11 Software Citation Working Group ``Software Citation Principles,'' FORCE2016 Website, \url{https://www.force11.org/software?citation?principles}, 2016. Accessed: 2016-07-10.
\bibitem{bib3} 
FORCE11 Software Citation Working Group, GitHub repository, \url{https://github.com/force11/force11-scwg}.  Accessed: 2016-07-10.
\bibitem{bib4} 
A.~Smith AM, D.~S.~Katz, K.~E.~Niemeyer, and FORCE11 Software Citation Working Group, “Software Citation Principles,” PeerJ Preprints 4:e2169v2, 2106. \url{https://doi.org/10.7287/peerj.preprints.2169v2}.

>>>>

\usepackage{flushend} % equalizes columns on last page

@@

The final draft paper was then submitted to  PeerJ Computer Science, published as a PeerJ preprint, and posted on the FORCE11 website \cite{bib2}. Initial review comments were returned July 8, 2016, and the working group chairs recently (August 1, 2016) submitted a revised version, and updated the PeerJ preprint \cite{bib4}. Our goal is to have a final version of the paper accepted by WSSSPE4.

@@

\bibitem{bib1}
FORCE11 Software Citation Working Group, ``Software citation use cases,'' \url{https://docs.google.com/document/d/1dS0SqGoBIFwLB5G3HiLLEOSAAgMdo8QPEpjYUaWCvIU}, 2016. Accessed: 2016-07-10.
\bibitem{bib2} 
A.~M.~Smith AM, D.~S.~Katz, K.~E.~Niemeyer, and FORCE11 Software Citation Working Group ``Software Citation Principles,'' FORCE2016 Website, \url{https://www.force11.org/software?citation?principles}, 2016. Accessed: 2016-07-10.
\bibitem{bib3} 
FORCE11 Software Citation Working Group, GitHub repository, \url{https://github.com/force11/force11-scwg}.  Accessed: 2016-07-10.
\bibitem{bib4} 
A.~Smith AM, D.~S.~Katz, K.~E.~Niemeyer, and FORCE11 Software Citation Working Group, “Software Citation Principles,” PeerJ Preprints 4:e2169v2, 2106. \url{https://doi.org/10.7287/peerj.preprints.2169v3}.
